The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/main.tex
Ok on pause for now
[frontrunning] fix appendix figure placements

%Possibly remove this figure due to page limit
\begin{figure}[t]
\centering
\includegraphics[width=0.3\linewidth]{figures/cryptokittie842912.png}
\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
\end{figure}

@@

%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}

Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum.

@@

\section{Commit-and-Reveal}

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
\caption{\scriptsize Commit and Reveal. User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment. \label{fig:commitReveal}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c

>>>>

%Possibly remove this figure due to page limit
\begin{figure}[!htb]
\centering
\includegraphics[width=0.3\linewidth]{figures/cryptokittie842912.png}
\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
\end{figure}

@@

%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum}]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}

Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum. \\

@@

\section{Commit-and-Reveal} \label{app:cr}

\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
\caption{\scriptsize Commit and Reveal. User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment. \label{fig:commitReveal}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c
